Lock-free Skiplist-based Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-03-13 paper/paper.tex
Minor corrections & additions
TODO note
Notes and relaxed introduction

\begin{figure}[h]
\begin{lstlisting}
struct node_t {
  [...] /**< Standard node members as above. */
  atomic<bool> deleted; /**< Initially false. */
  time_t timestamp;
  lock_t locks[level + 1];
};
\end{lstlisting}
\caption{\citeauthor{shavit2000skiplist} structure.}
\label{fig:slsl}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
struct node_t {
  [...] /**< Standard node members as above. */
  size_t valid_level;
  node_t *prev;
};
\end{lstlisting}
\caption{\citeauthor{sundell2003fast} structure.}
\label{fig:slsl}
\end{figure}

@@

\subsection{Linden \& Jonsson}

@@

\subsection{Wimmer}
\subsection{SprayList}

@@

% TODO: Figures, interpretation. Mention that Noble requires pointers -> new/delete.
% Better hardware description - see SprayList section 4.
% Note: Strong degradation of noble PQ with growing initial size.

>>>>

\begin{figure}[h]
\begin{lstlisting}
struct node_t {
  [...] /**< Standard node members as above. */
  atomic<bool> deleted; /**< Initially false. */
  time_t timestamp;
  lock_t locks[level + 1];
};
\end{lstlisting}
\caption{\citeauthor{shavit2000skiplist} structure.}
\label{fig:shavitsl}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
struct node_t {
  [...] /**< Standard node members as above. */
  size_t valid_level;
  node_t *prev;
};
\end{lstlisting}
\caption{\citeauthor{sundell2003fast} structure.}
\label{fig:sundellsl}
\end{figure}

@@

\subsection{Linden \& Jonsson} \label{sec:linden}

\begin{figure}[h]
\begin{lstlisting}
struct node_t {
  [...] /**< Standard node members as above. */
  atomic<bool> inserting;
};
\end{lstlisting}
\caption{\citeauthor{linden2013skiplist} structure.}
\label{fig:lindensl}
\end{figure}

 % Mention the BoundOffset parameter (p17), and benching using Fraser-based impls.

@@

The body of work discussed in previous sections
creates the impression that limits of strict, deterministic priority queues have been reached.
In particular, \citeauthor{} conclude that scalability is solely limited by \lstinline|DeleteMin|,
and that less than one modified memory location per thread and operation would have to be read
in order to achieve improved performance \cite{}. % TODO: Cites for this entire section.

Recently, relaxation of provided guarantees have been investigated as another method of reducing
contention and improving disjoint-access parallelism.
For instance, k-FIFO queues \cite{} have achieved considerable
speed-ups compared to strict FIFO queues by allowing \lstinline|Dequeue| to return elements
up to k positions out of order.

Relaxation has also been applied to concurrent priority queues with some success, and in the following
sections we discuss two different approaches.

\subsection{Wimmer} \label{sec:wimmer}
\subsection{SprayList} \label{sec:spraylist}

@@

% TODO: Figures, interpretation. Mention that Noble requires pointers -> new/delete.
% Better hardware description - see SprayList section 4, Linden p16.
% Note: Strong degradation of noble PQ with growing initial size.
% Standard PQ benchmarking methodology, cite linden + ??.
% Drop-off when using more than 1 socket, Linden p17.
